Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-12-12 cav2017/cav2017.tex

Program synthesisers are an ideal fit for synthesis of parametric
controllers since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilizing continuous-time
plants with polynomial dynamics.  The work extends to its application on
affine systems, finding its major challenge in the hardness of solving
linear arithmetic with the state-of-the-art SMT solvers.  Since this
approach uses switching states instead of linear dynamics in the digital
controller, it entirely circumvents the FWL problem.  It is also not
suitable for the kind of control we seek to synthesize.  We require a
combination of a synthesis engine with a control verification tool that
addresses the challenges presented here in the form of FWL effects and
stability measures for LTI SISO controllers.  We take the former
from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161},
while enhancing the procedure by evaluating the quantization effects of the
Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
representation of the continuous dynamics.

>>>>

Program synthesisers are an ideal fit for synthesis of parametric
controllers since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilizing continuous-time
plants with polynomial dynamics.  The work extends to its application on
affine systems, finding its major challenge in the hardness of solving
linear arithmetic with the state-of-the-art SMT solvers.  Since this
approach uses switching states instead of linear dynamics in the digital
controller, it entirely circumvents the FWL problem.  It is also not
suitable for the kind of control we seek to synthesize.
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesizing continuous-time switching
controllers that guarantee reach while stay properties of a closed
loop system. The solution is based on synthesizing control Lyapunov
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode.

We require a
combination of a synthesis engine with a control verification tool that
addresses the challenges presented here in the form of FWL effects and
stability measures for LTI SISO controllers.  We take the former
from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161},
while enhancing the procedure by evaluating the quantization effects of the
Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
representation of the continuous dynamics.

### 2016-12-12 paper/reply.tex

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Pscal).}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} We did include an upper bound for both the
bit width and execution time. Given an arbitrarily high precision and given
unlimited execution time, the engine will always succeed.}
\end{quote}

>>>>

\begin{quote}
\textcolor{blue}{\textbf{Response:} Number of remains within 1-2 per CEGIS step
for benchmarks in which two-step engine succeeds. However, there are 3-5 plant
precision increases using our current implementation. Our CEGIS implementation
spends 95\% of its runtime in the synthesis phase, and only 5\% in the
verification phase. Improvements in the  precision increase heuristic and the
synthesis phase will thus benefit the runtime most.}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} As stated in section 4.3, we did bound the
runtime per benchmark in our experiment, which was the reason behind the failure
to synthesise benchmark 4. We also limited our experiment to 64 bits word width,
but as stated in 4.3 CBMC supports arbitrary precision fixed point types which,
given sufficient runtime, can be used to synthesise the missing controller.}
\end{quote}
